Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex

We have implemented, optimized, and evaluated an analysis framework
supporting higher-order functions, state, first-class control,
compound data, and a large number of primitive kinds of data and
operations such as floating point, complex, and exact rational
arithmetic.  The analysis is evaluated against a suite of benchmarks
drawn from the literature.
%
For each benchmark, we collect analysis times, peak memory usage, and
the rate of states-per-second explored by the analysis for each of the
optimizations discussed in section~\ref{sec:opt}, culmulatively
applied.  The analysis is stopped after consuming 30 minutes of time
or 1 gigabyte of space.  When presenting \emph{relative} numbers, we
use the timeout limits as a lower bound on the actual time required,
thus giving a conservative estimate of improvements.

>>>>

We have implemented, optimized, and evaluated an analysis framework
supporting higher-order functions, state, first-class control,
compound data, and a large number of primitive kinds of data and
operations such as floating point, complex, and exact rational
arithmetic.  The analysis is evaluated against a suite of benchmarks
drawn from the literature.
%
For each benchmark, we collect analysis times, peak memory usage, and
the rate of states-per-second explored by the analysis for each of the
optimizations discussed in section~\ref{sec:opt}, cumulatively
applied.  The analysis is stopped after consuming 30 minutes of time
or 1 gigabyte of space.  When presenting \emph{relative} numbers, we
use the timeout limits as a lower bound on the actual time required,
thus giving a conservative estimate of improvements.
